TEMPERATURES AND METALLICITIES FOR 10,000 M DWARFS\\ IN THE \apogee\ SURVEY

### 2018-08-13 paper/draft.tex
validation description
no subsection
more JB to-do items

\author[0000-0003-2866-9403]{David W. Hogg}
\affil{Max-Planck-Institut f\"ur Astronomie, K\"onigstuhl 17, D-69117 Heidelberg, Germany}
\affil{Center for Computational Astrophysics, Flatiron Institute, 162 Fifth Ave, New York, NY 10010, USA}
\affil{Center for Cosmology and Particle Physics, Department of Physics, New York University, 726
Broadway, New York, NY 10003, USA}
\affil{Center for Data Science, New York University, 60 Fifth Ave, New York, NY 10011, USA}

@@

%%==========================================================================================
\section{Methods} \label{sec:cannon}

\subsection{\thecannon\: A Data-Driven Approach}

@@

Quadratic label vectors:
	\[\ell_{n} = [1, \, SPT, \, SPT^{2}] \]
	\[\ell_{n} = [1, \, T_{\rm eff}, \, [Fe/H], \, T_{\rm eff} \cdot [Fe/H], \, [Fe/H]^{2}] \]

The training step description...

Test step description...

@@

%---------------------------
\begin{figure}[ht]
\plotone{figures/aspcap_cannon_validation.png}
\caption{Validation test of \cannon\ temperatures (left), as compared to \aspcap\ temperatures (right) using three different color-temperature relations derived from \citealt{Mann:2015}, \citealt{Casagrande:2008}, and \citealt{Boyajian:2013}. For all three relations  \label{fig:aspcap_cannon_validation}}
\end{figure}

>>>>

\author[0000-0003-2866-9403]{David W. Hogg}
\affil{Max-Planck-Institut f\"ur Astronomie, K\"onigstuhl 17, D-69117 Heidelberg, Germany}
\affil{Center for Cosmology and Particle Physics, Department of Physics, New York University, 726
Broadway, New York, NY 10003, USA}
\affil{Center for Data Science, New York University, 60 Fifth Ave, New York, NY 10011, USA}
\affil{Center for Computational Astrophysics, Flatiron Institute, 162 Fifth Ave, New York, NY 10010, USA}

@@

%%==========================================================================================
\section{Method}\label{sec:cannon}

@@

Quadratic label vectors for the two models that we will build:
\begin{eqnarray}
\ell_{n} &=& [1, \, SPT, \, SPT^{2}]
\\
\ell_{n} &=& [1, \, T_{\rm eff}, \, [Fe/H], \, T_{\rm eff} \cdot [Fe/H], \, [Fe/H]^{2}]
,
\end{eqnarray}
where the first is for JB WHAT and the second is for JB WHAT?

JB: The training step description: OPTIMIZE THETA AT FIXED LABELS.

JB: Test step description: OPTIMIZE LABELS AT FIXED THETA.

Thus \thecannon\ is both a generative model for the stellar spectra, and a method for obtaining
labels from spectra. In the training step, the regression is designed to predict spectral pixels
given labels, by learning zeroth, first, and second derivatives of the data with respect to
the labels. In the test step, the regression is designed to predict labels given the spectral
derivatives.

@@

%---------------------------
\begin{figure}[ht]
\plotone{figures/aspcap_cannon_validation.png}
\caption{Validation test of \cannon\ temperatures (left), as compared to \aspcap\ temperatures (right) using three different color-temperature relations derived from \citealt{Mann:2015}, \citealt{Casagrande:2008}, and \citealt{Boyajian:2013}. We find \cannon\ temperatures to be significantly more consistent with all three relations in terms of bias and scatter. \label{fig:aspcap_cannon_validation}}
\end{figure}
